Probabilistic Model of Bilateral Lymphatic Spread in Head and Neck Cancer

### 2024-04-16 manuscript.qmd
run new pipeline

for model in ["ipsi", "contra", "bilateral", "midline"]:
  history = pd.read_csv(f"models/{model}/history.csv").set_index("steps")
  for i, column in enumerate(history.columns):
    history.plot(y=column, ax=axes[i], label=model)
    axes[i].autoscale(enable=True, tight=True, axis="x")
    axes[i].set_ylabel(label_map[column])
    axes[i].xaxis.set_major_formatter(ticker.FuncFormatter(custom))
    axes[i].set_xlabel(r"steps [$\times 10^3$]")

@@

model = shared.get_model(which="midline")
scenarios_config = utils.load_yaml_params("scenarios.yaml")
scenarios = Scenario.list_from_params(scenarios_config)

@@

mi = pd.MultiIndex.from_product(
  [[False, True]] * len(midline_model.ext.ipsi.graph.lnls),
  names=midline_model.ext.ipsi.graph.lnls.keys(),
)
series = pd.Series(midline_model.ext.ipsi.state_dist(), index=mi)
upsetplot.plot(series)
plt.show()
```

>>>>

for model in ["contra", "bilateral", "midline"]:
  history = pd.read_csv(f"models/{model}/history.csv").set_index("steps")
  for i, column in enumerate(history.columns):
    history.plot(y=column, ax=axes[i], label=model)
    axes[i].autoscale(enable=True, tight=True, axis="x")
    axes[i].set_ylabel(label_map[column])
    axes[i].xaxis.set_major_formatter(ticker.FuncFormatter(custom))
    axes[i].set_xlabel(r"steps [$\times 10^3$]")

@@

model = shared.get_model(which="midline")
scenarios_config = utils.load_yaml_params("scenarios/base.yaml")
scenarios = Scenario.list_from_params(scenarios_config)

@@

mi = pd.MultiIndex.from_product(
  [[False, True]] * len(midline_model.ext.ipsi.graph.lnls),
  names=midline_model.ext.ipsi.graph.lnls.keys(),
)
series = pd.Series(midline_model.ext.ipsi.state_dist(), index=mi)
upsetplot.plot(
  series,
  sort_by="cardinality",
  sort_categories_by="-input",
)
plt.show()
```
